localhierarchy

### 2025-10-16 README.Rmd
package related fixes

---
title: "localHierarchy"
output: github_document
---

@@

# Background

@@

The `localHierarchy` R package provides functionality for fitting Bayesian hierarchical models in settings where both global and local estimation is required. The package provides R functions and Stan model components to support global modeling, in which all parameters in hierarchical models are estimated, and local modeling, in which parameters are estimated for only one or a small number of populations, using fixed values from a global model fit.

@@

# Installation

-   `localHierarchy` depends on `cmdstanr:` Instructions for installing `cmdstanr` are available in their [Getting started](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) guide.

-   Install `localHierarchy` from Github: `remotes::install_github("AlkemaLab/localhierarchy")`

# Examples

>>>>

---
title: "localhierarchy"
output: github_document
---

@@

## Background

@@

The `localhierarchy` R package provides functionality for fitting Bayesian hierarchical models in settings where both global and local estimation is required. The package provides R functions and Stan model components to support global modeling, in which all parameters in hierarchical models are estimated, and local modeling, in which parameters are estimated for only one or a small number of populations, using fixed values from a global model fit.

@@

## Installation

-   `localhierarchy` depends on `cmdstanr:` Instructions for installing `cmdstanr` are available in their [Getting started](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) guide.

-   Install `localhierarchy` from Github: `remotes::install_github("AlkemaLab/localhierarchy")`

## Examples
